### 2022-09-20 README.Rmd
srr tags removed

## Installation
You can install the latest stable release from [CRAN](https://cran.r-project.org/package=melt).
```{r eval = FALSE}
install.packages("melt")
```
You can install the latest development version from
[Github](https://github.com/ropensci/melt) or [R-universe](https://ropensci.r-universe.dev/ui#package:melt).
```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("ropensci/melt")

install.packages("melt", repos = "https://ropensci.r-universe.dev")
```

>>>>

## Installation
You can install the latest stable release from [CRAN](https://cran.r-project.org/package=melt).
```{r eval = FALSE}
install.packages("melt")
```
You can install the latest development version from
[GitHub](https://github.com/ropensci/melt) or [R-universe](https://ropensci.r-universe.dev/ui#package:melt).
```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("ropensci/melt")
```

```{r eval = FALSE}
install.packages("melt", repos = "https://ropensci.r-universe.dev")
```
